Start with the literature: assessthe empirical evidence for the relationship between ter-rorism and political attitudes

### 2024-02-15 outputs/paper/paper.qmd
edits

dat <- read_excel("/cloud/project/raw/data/02-metaanalysis-data.xlsx", sheet = "Data", 
                  col_names = TRUE, skip = 3)

@@

ggarrange(StudyYear, PubYear, 
          TerrorMeasures, TerrorType,
          labels = c("(A)", "(B)", "(C)", "(D)"),
          font.label = list(size = 10, color = "black"),
          widths = 10,
          heights = 10,
          ncol = 2, nrow = 2) #arrange all plots

@@

knitr::kable(
  tibble(OutcomeType = c("Outgroup hostility","Conservative shift","Rally effects"),
         k = c(645,728,360),
         j = c(126,144,72),
         Zr = c(0.126,0.132,0.090),
         LBCI = c("[0.094;0.159]","[0.108;0.156]","[0.055;0.127]")
  )
)
```

>>>>

dat <- read_excel("/cloud/project/inputs/data/02-metaanalysis-data.xlsx", sheet = "Data", 
                  col_names = TRUE, skip = 3)

@@

ggarrange(StudyYear, PubYear, 
          TerrorMeasures, TerrorType,
          labels = c("(A)", "(B)", "(C)", "(D)"),
          font.label = list(size = 10, color = "black"),
          widths = 10,
          heights = 15,
          ncol = 2, nrow = 2) #arrange all plots

@@

knitr::kable(
  tibble(OutcomeType = c("Outgroup hostility","Conservative shift","Rally effects"),
         k = c(645,728,360),
         j = c(126,144,72),
         Zr = c(0.126,0.132,0.090),
         LBCI = c("[0.094;0.159]","[0.108;0.156]","[0.055;0.127]")
  ),
  caption = "Relationship between Terrorism and Political Attitudes"
)
```
